On Secure Delegation of SampBQP with a Classical Client

### 2020-01-05 qpip.tex
Updates from Overleaf
Implement one of Han-Hsuan's suggestions

\begin{observation}
	\label{ProtoGroundStateCheck}
	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{observation}
\begin{proof}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{proof}
\hannote{something. pull protocol out?}
\begin{theorem}
    \label{QPIP1thm}
	For any $L\in\SampBQP$,  there exists a $\QPIP_1$ protocol for $L$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{theorem}
\begin{proof}
	Set the following variables
	\begin{itemize}
		\item $\varepsilon=T^{-c}$
		\item $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\item $n$ large enough so the following quantities are negligible in $\varepsilon$ by the Chernoff bound:
			\begin{itemize}
				\item[$\circ$] $P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$
				\item[$\circ$] $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$
			\end{itemize}
		\item $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
	\end{itemize}

	With these parameters, we claim that \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} does what is required.
	\floatname{algorithm}{Protocol}
	\begin{algorithm}
		\caption{ $\QPIP_1$ protocol for $\SampBQP$}
		\label{ProtoQPIP1}
		\begin{algorithmic}[1]
			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
			\State The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
			\State $c\gets0$
			\State $y\gets\bot$
			\For{$i\gets1, N$}
			    \If{Copy is for checking}
				\State The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
			    \If{Test passes}
			        $c\gets c+1$
			    \EndIf
			    \ElsIf{Copy is for outputting}
			    \State The verifier measures the copy in standard basis
			    \If{measurement result of the clock register $\geq\frac{T}{2}$}
			        \If{$y=\bot$}
			            \State $y\gets$ measurement result of the data register
                    \EndIf
			    \EndIf
			    \Else
			    \State The verifier measures the entire register in standard basis
			    \EndIf
			\EndFor
			\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
			\If{$y\ne\bot$}
			\State output $y$
			\Else
			\State Reject
			\EndIf
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

	It clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover that has at least $\delta$ probability to be accepted. Let $\sigma$ be the state the prover sends to the verifier.

@@

Let $\varepsilon>0$. Pick $N$ large enough so that by geometric probability getting a 
We pick $h$ the same way as we'd decide the measurement basis as in \Ethan{TODO ref protocol 2}.

>>>>

\begin{observation}
	\label{ProtoGroundStateCheck}
	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{observation}
\begin{proof}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{proof}

Now we present \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}}, a $\QPIP_1$ protocol for any $\SampBQP$ problem with inverse polynomial error in circuit size.

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoQPIP1}
	\begin{algorithmic}[1]
		\Procedure{QPIP1}{$C, x, c$}
		\State Let $\varepsilon=T^{-c}$
		\State Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\State Let $n$ be large enough so both $P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ and $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ are negligible in $\varepsilon$ by Chernoff bound
		\State Let $N$ be large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.

		\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
		\State The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
		\State $c\gets0$
		\State $y\gets\bot$
		\For{$i\gets1, N$}
			\If{Copy is for checking}
			\State The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
			\If{Test passes}
				$c\gets c+1$
			\EndIf
			\ElsIf{Copy is for outputting}
			\State The verifier measures the copy in standard basis
			\If{measurement result of the clock register $\geq\frac{T}{2}$}
				\If{$y=\bot$}
					\State $y\gets$ measurement result of the data register
				\EndIf
			\EndIf
			\Else
			\State The verifier measures the entire register in standard basis
			\EndIf
		\EndFor
		\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
		\If{$y\ne\bot$}
		\State output $y$
		\Else
		\State Reject
		\EndIf
		\Else
		\State Reject
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

\begin{theorem}
    \label{QPIP1thm}
	For any $L\in\SampBQP$, \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} is a protocol for $L$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{theorem}
\begin{proof}
	It clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover that has at least $\delta$ probability to be accepted. Let $\sigma$ be the state the prover sends to the verifier.

@@

Let $\varepsilon>0$. Pick $N$ large enough so that by

We pick $h$ the same way as we'd decide the measurement basis as in \Ethan{TODO ref protocol 2}.
